---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README_",
  out.width = "100%"
)
```

# NBASTARS

<!-- badges: start -->
<!-- badges: end -->

The goal of NBASTARS package is to assist with the machine learning task of predicting NBA All stars using the NBA all stars data set from kaggle.

## Installation

You can install the development version of NBASTARS from [GitHub](https://github.com/DSCI-310/dsci-310-group-14-pkg) with:

``` {r}
# install.packages("devtools")
devtools::install_github("DSCI-310/dsci-310-group-14-pkg")
```

## Examples

This is a basic example which shows you how to use the select_to_from function which filters a specified variable using a range:

```{r select}
library(NBASTARS)
## basic example code
selected <- select_to_from(mtcars,mpg,21,22.8)
head(selected)
```

This is a basic example which shows you how to use the proportion function which summarizes the specified variable and returns a percentage proportion:

```{r prop}
## basic example code
proportion(mtcars,vs)

```
This is a basic example to use the split data function which splits the dataset and saves it into two global variables "data_training" and "data_testing"

```{r split}
## basic example code
split_data(mtcars,0.7,"vs")
head(data_testing)
head(data_training)
```

Here is a quick example of using the visualize_knn function which shows us a elbow graph for K selection when using KNN prediction models:

```{r k selector}
K <- c(1,2,4,5,10,18,25)
accuracy <- c(0.2,0.4,0.6,0.7,0.4,0.2,0.3)
df <- data.frame(K,accuracy)
visualize_knn(df,K,accuracy,"example selector")
```




