---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(NBASTARS)
```

This document contains documentation and example on how to use the NBASTARS package to assist you in performing data analysis and modelling on the NBA players dataset.

NBASTARS package has four main functions:
1. select_to_from() will apply a filter using a numeric variable dataset and a specified range
2. proportion() will summarize categorical data and return a summary view with percentage proportions
3. split_data() streamlines the data splitting process for machine learning into a test and training dataset
4. visualize_knn() visualizes knn accuracy data to help you select a k by producing a elbow graph

## Data: MTCARS

```{r load}
head(mtcars)
```
To showcase the package, we will be using the built-in mtcars dataset

## Functions

### 1. select_to_from()
select_to_from() first requires a data frame. Then you would need to specify a specific numerical column, and two numbers which represents the numerical range you wish to filter the column from and to.

For example, we can filter the different cars in mtcars by their miles per gallon from 21 to 22.8.
```{r select example}
select_to_from(mtcars, mpg, 21, 22.8)
```
### 2. proportion()
proportion() Helps you with basic exploration of categorical variables by summarize categorical data and returning the percentage of the data that falls under each category. proportion() requires you need specify the dataset and the categorical variable in that dataset.

For example, we can check how many cars have v shape engines with the mtcars dataset:
```{r prop example}
proportion(mtcars, vs)
```
### 3. split_data()
split_data() Helps you split your dataset to into a training and testing dataset in order to help you validate your models. split_data() requires a dataset, a specific split percentage and lastly a specified strata which should be the variable you are prediciting for. The strata will ensure the split ensures both dataset have a similar proportions of the predicting variable.

Below illustrates how to use the function. We specified 0.7 training to testing split and using the v-type engine variable as the strata. We can see the function saved the split dataset into two global variables called "data_training" and "data_testing".
```{r split example}
split_data(mtcars, 0.7, "vs")
head(data_training)
head(data_testing)
```

### 4. visualize_knn()
visualize_knn() helps you generate a elbow graph for the purposes of selecting a K value for your knn model. visualize_knn requires you first check the responding accuracy of each K value. We have created a psuedo dataset to illustrate this function's usage.
```{r knn example,fig.width=9}
K <- c(1, 2, 4, 5, 10, 18, 25)
accuracy <- c(0.2, 0.4, 0.6, 0.7, 0.4, 0.2, 0.3)
df <- data.frame(K, accuracy)
visualize_knn(df, K, accuracy, "example elbow graph")
```
